The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-08-20 paper/ms.tex
more tim edits

In this Section we will discuss the methods used for characterizing our new benchmark stars. We have obtained smear light curves for our sample of red giant stars with the \texttt{keplersmear} pipeline as described in Section~\ref{photometry}, performed asteroseismology on all of these to extract \numax and therefore \logg as described in Section~\ref{asteroseismology}, and combined these with TRES spectra to obtain chemical abundances as described in Section~\ref{spectroscopy}.

@@

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ which were unobserved for more than $8$ quarters, including those stars which were entirely unobserved. A number of these lay just at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}. The \kepler satellite rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. Aside from the restriction on stars falling on the edge of a chip like this or otherwise, the addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$.

>>>>

We have obtained smear light curves for our sample of red giant stars with the \texttt{keplersmear} pipeline as described in Section~\ref{photometry}, performed asteroseismology on all of these to extract \numax and therefore \logg as described in Section~\ref{asteroseismology}, and combined these with TRES spectra to obtain chemical abundances as described in Section~\ref{spectroscopy}.

@@

We selected as our sample all stars on-silicon in \kepler with $Kp<9$ that were targeted for fewer than $8$ quarters, including those stars that were entirely unobserved. A number of these lay at the edge of a detector, with the result that in some cadences the centroid of the star did not lie on the chip; light curves from these targets were found to be of extremely low quality and all of these objects were discarded. After applying these criteria we obtained a list of 102 targets, which are listed in Table~\ref{all_stars} in order of their \kepler magnitude $Kp$ together with their spectral type from SIMBAD, \gaia~DR2 source identifiers, apparent~$G$ magnitudes and distances from \citet{gaiadists}, the quarters for which the stars were observed, and whether spectroscopy is available as in Section~\ref{spectroscopy} and Table~\ref{stellar_props}. The \kepler satellite rotates between quarters, so that it cycles through four orientation `seasons' each rotated from the last by $90^{\circ}$. Some stars did not land on silicon for all seasons: we have only one season of HD~179394; two for HD~187277, HD~226754, V554~Lyr, and BD+47~2891; and three for BD+43~3064. Aside from the restriction on stars falling on the edge of a chip like this or otherwise, the addition of our sample to the conventionally-observed stars makes the \kepler survey magnitude-complete down to $Kp=9$.
